% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.34in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\addtolength{\topmargin}{-.26in}
\addtolength{\oddsidemargin}{-.15in}
\addtolength{\evensidemargin}{-.15in}
\addtolength{\textheight}{3cm}


%\addtolength{\topmargin}{-.56in}
%\addtolength{\evensidemargin}{-.5in}
%\addtolength{\oddsidemargin}{-.35in}
%\addtolength{\voffset}{0cm}
%\addtolength{\textheight}{5cm}

%\addtolength{\bottom}{-.25in}

\begin{document} 
 \name{Mark Kamuda\\[12pt]} % the \\[12pt] adds a blank line after name

% \address{{\bf Office Address} \\ 104 S. Wright St, Room 119 \\ Urbana, IL 61820\\ (405)509.4584 \\ stinntt2@illinois.edu }
 
\address{{\bf Home Address} \\ 461 Springside Lane  \\ Buffalo Grove, IL 60089 }

%\address{{\bf Contact} \\ e-mail: stinnettjacob@gmail.com  \\ website: stinnett.github.io  \\ (405)509.4584 }

\address{{\bf Contact} \\ e-mail: kamuda1@illinois.edu \\ work: (847) 917-0302 }

 
\begin{resume} 
 
%\section{Objective} 
%Auditing/Analysis of Operations 

\section{Citizenship}

U.S.A.

\section{Education} 

\vspace{-.05in}

M.S. in Nuclear, Plasma, and Radiological Engineering, University of\ Illinois at Urbana-Champaign  \hfill \textbf{2017}

\begin{itemize}
\item ``Automated Isotope Identification Algorithm Using Artificial Neural Networks.''
\item Advisor: Professor Clair J. Sullivan
\end{itemize}

\vspace{-.05in}

B.S. in Nuclear, Plasma, and Radiological Engineering, University of\ Illinois at Urbana-Champaign \hfill  \textbf{2014}
 

\section{Experience}

 
 {\bf PhD Research Fellow,} UIUC, Urbana, IL \hfill \textbf{May 2017 - May 2019 (expected) }
 \begin{itemize} \itemsep -3pt  % reduce space between items
 \item Applied machine learning methods to automated isotope identification
 \item Advisor: Professor Kathryn D. Huff
 \end{itemize} 
 
 
 {\bf Guest Scientist,} Los Alamos National Laboratory, Los Alamos, NM \hfill \textbf{Summer 2015}
 \begin{itemize} \itemsep -3pt  % reduce space between items
 \item Analyzed legacy spectroscopic data to increase the accuracy of the measured gamma-ray branching ratios for $^{147}$Nd 
 \item Performed gamma-ray spectroscopy measurements at the Nevada National Security Site
 \end{itemize} 
 
\vspace{-.05in}
 
 {\bf Teaching Assistant,} UIUC, Urbana, IL \hfill \textbf{Spring 2013, Spring 2014} 

 \begin{itemize} \itemsep -3pt  % reduce space between items
 \item Nuclear Weapons and Arms Control (PHYS 280)
 \end{itemize}

\vspace{-.05in}
 
 {\bf Undergraduate Research Assistant,} UIUC, Urbana, IL \hfill  \textbf{2013-2014}
\begin{itemize} \itemsep -3pt %reduce space between items
\item Undergraduate Research Assistant to Dr. Clair J. Sullivan: Set up and calibrated radiation detectors for research experiments
\item Measured the detector response and efficiency of a NaI detector  
\end{itemize}

\vspace{-.05in}



 {\bf Engineering Outreach Society, President,} UIUC, Urbana, IL \hfill \textbf{Aug 2013 - May 2014}
 \begin{itemize} \itemsep -3pt  % reduce space between items
 \item President of the Engineering Outreach Society (EOS), a University recognized Registered Student Organization (RSO)
 \item Managed a volunteer club of about 50 students 
 \item Organized weekly science demonstrations at two local elementary schools

 \end{itemize} 









 {\bf Guest Scientist,} Brookhaven National Laboratory, Brookhaven, NY \hfill \textbf{Summer 2013}
 \begin{itemize} \itemsep -3pt  % reduce space between items
 \item Simulated a novel collimator design in Geant4
 \item Analyzed the performance of the novel collimator for a specific imaging application 
 \item Presented our work in a poster and published article 
 \end{itemize} 



%\section{Skills}

\section{Publications}
%J. Stinnett and C.J. Sullivan.  ``An Automated Isotope Identification Algorithm using Bayesian Statistics.''  \textit{IEEE Transactions on Nuclear Science}, In Publication. \hfill 2014
%

M. Kamuda and C.J. Sullivan . An Automated Isotope Identification and Quantification Algorithm for Isotope Mixtures in Low-Resolution Gamma-ray Spectra. \textit{Radiation Physics and Chemistry}. In review. \hfill \textbf{2018}

\vspace{-.05in}

M. Kamuda.  ``Automated Isotope Identification Algorithm Using Artificial Neural Networks''.  \textit{MS Thesis}.  University of Illinois at Urbana-Champaign. \hfill \textbf{2017}

M. Kamuda, J. Stinnett, and C.J. Sullivan . Automated Isotope Identification Algorithm Using Artificial Neural Networks. \textit{IEEE Transactions on Nuclear Science}. \hfill \textbf{2017}


J. Mattingly, J. Hutchinson, C. Sullivan, J. Stinnett , M. Kamuda, M. Alamaniotis, B. Simms, J. Mueller, J. Newby, J. Linkous, S. Pozzi, K. Polack, M. Hamel, Z. He, D. Goodman, and M. Streicher.  "CNEC and CVT Subcritical Experiments with Category I Special Nuclear Material at the Nevada National Security Site Device Assembly Facility." \textit{Institute of Nuclear Materials Management Conference Record}. \hfill \textbf{2016}



 Mark Kamuda, Yonggang Cui, Terry Lall, Jim Ionson, Giuseppe S. Camarda, Anwar Hossainm, Ge Yang, Utpal N. Roy, and Ralph B. James. Modeling Of A Slanted-hole Collimator In A Compact Endo-cavity Gamma Camera. \textit{SPIE Proceedings}. \hfill \textbf{2013}








\section{Conference Presentations}

M. Kamuda. `'Uranium Enrichment Measurements Using an
Artificial Neural Network.'' \textit{CVT Workshop}. Ann Arbor, MI.  \hfill \textbf{2017}

M. Kamuda and C.J. Sullivan. `'Automated Isotope Identification Algorithm Using Artificial Neural Networks.'' \textit{UPR}. Walnut Creek, CA.  \hfill \textbf{2017}


M. Kamuda and C.J. Sullivan. `'An Automated Isotope Identification and Quantification Algorithm for Isotope Mixtures in Low-Resolution Gamma-ray Spectra.'' \textit{IRRMA-X}. Chicago, IL.  \hfill \textbf{2017}

M. Kamuda, J. Stinnett, C.J. Sullivan. `'Peak Quantification with Neural Networks for Low-Resolution NaI Spectra.'' \textit{IEEE Nuclear NSS/MIC}. Strasbourg, France.  \hfill \textbf{2016}


M. Kamuda and C.J. Sullivan. `'An Automated Isotope Identification and Quantification Algorithm for Isotope Mixtures in Low-Resolution Gamma-ray Spectra.'' \textit{SORMA}. Berkeley, CA.  \hfill \textbf{2016}


M. Kamuda, M.M. Watson, and C.J. Sullivan. `'Information Barriers based on Enhanced Automated Isotope Identification.'' \textit{UITI}. Ann Arbor, MI.  \hfill \textbf{2015}






\section{Guided Discussions}

M. Kamuda and J. Wilson. `'Data Mining and Machine Learning.'' \textit{The Hacker Within}. Champaign-Urbana, IL.  \hfill \textbf{February, 2018}

M. Kamuda. `'Natural Language Processing.'' \textit{The Hacker Within}. Champaign-Urbana, IL.  \hfill \textbf{November, 2017}

M. Kamuda. `'Introduction to TensorFlow.'' \textit{The Hacker Within}. Champaign-Urbana, IL.  \hfill \textbf{September, 2017}


\section{Programming}
Python (Numpy, Pandas, Matplotlib, Scikit-learn, Jupyter Notebooks, Tensorflow), LaTeX, JavaScript, MATLAB, Mathematica, MCNP6, Geant4
 
\end{resume} 
\end{document} 



